### 2013-09-12 legend.tex
Merge branch 'master' of svn.ais.uni-bonn.de:u/amueller/icra_2014_nyu
git-svn-id: https://svn.ais.uni-bonn.de/svn/staff/publications/icra_2014_mueller_nyu@4357 b2511e17-9ac0-488b-bc21-1d6d82e5baa2

\documentclass{standalone}
\usepackage{color}
\usepackage{tikz}

\definecolor{structure}{RGB}{185, 202, 202}
\definecolor{prop}{RGB}{227, 172, 0}
\definecolor{furniture}{RGB}{255, 94, 28}
\definecolor{ground}{RGB}{9, 68, 83}
%[``structure'', ``prop'', ``furniture'', ``ground'' , ``void'']

\begin{document}
    \begin{tikzpicture}
        \matrix [column sep=.5cm]{%
        \node [rectangle, fill=ground, minimum width=.5cm,minimum height=.5cm] {};&
        \node [draw=none] {Ground};&
        \node [rectangle, fill=structure, minimum width=.5cm,minimum height=.5cm] {};&
        \node [draw=none] {Structure};&
        \node [rectangle, fill=furniture, minimum width=.5cm,minimum height=.5cm] {};&
        \node [draw=none] {Furniture};&
        \node [rectangle, fill=prop, minimum width=.5cm,minimum height=.5cm] {};&
        \node [draw=none] {Props};&
        \node [rectangle, fill=black, minimum width=.5cm,minimum height=.5cm] {};&
        \node [draw=none] {Void};\\
    };
    \end{tikzpicture}
\end{document}

### 2013-09-12 paper.tex
Merge branch 'master' of svn.ais.uni-bonn.de:u/amueller/icra_2014_nyu
git-svn-id: https://svn.ais.uni-bonn.de/svn/staff/publications/icra_2014_mueller_nyu@4357 b2511e17-9ac0-488b-bc21-1d6d82e5baa2

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%2345678901234567890123456789012345678901234567890123456789012345678901234567890
%        1         2         3         4         5         6         7         8

%\documentclass[letterpaper, 10 pt, conference]{ieeeconf}  % Comment this line out if you need a4paper

\documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4 paper

\IEEEoverridecommandlockouts                              % This command is only needed if 
                                                          % you want to use the \thanks command

\overrideIEEEmargins                                      % Needed to meet printer requirements.

% See the \addtolength command later in the file to balance the column lengths
% on the last page of the document

\makeatletter
\let\NAT@parse\undefined
\makeatother

% The following packages can be found on http:\\www.ctan.org
\usepackage{graphicx} % for pdf, bitmapped graphics files
\usepackage{epsfig}
\usepackage{refstyle}
%\usepackage{epsfig} % for postscript graphics files
%\usepackage{mathptmx} % assumes new font selection scheme installed
%\usepackage{times} % assumes new font selection scheme installed
\usepackage{amsmath} % assumes amsmath package installed
\usepackage{amssymb}  % assumes amsmath package installed
\usepackage{booktabs}
\usepackage{tabu}
\usepackage{tabularx}
\usepackage{graphicx}
\usepackage{tikz}
\usetikzlibrary{matrix}

%\usepackage[numbers]{natbib}
\usepackage[natbib, style=ieee]{biblatex}
\addbibresource{paper.bib}

\DeclareMathOperator*{\argmax}{arg\,max}

\title{\LARGE \bf
Learning Depth-Sensitive Conditional Random Fields for Semantic Segmentation of RGB-D Images
}

\author{Andreas C. M\"uller and Sven Behnke
\thanks{All authors are with the Autonomous Intelligent Systems Group, Univer-
        sity of Bonn, Germany. Email: amueller@ais.uni-bonn.de
    }}

\begin{document}

\maketitle
\thispagestyle{empty}
\pagestyle{empty}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
    We present a structured learning approach to semantic annotation of RGB-D
    images. 
    Our method learns to reason about spacial relations of objects and
    fuses low-level class predictions to a consistent interpretation of a
    scene. Our model incooporates color, depth and 3D scene features, on which
    an energy function is learned to directly optimize object class prediction using
    the loss-based maximum-margin principle of structural support vector machines.
    %With the proliferation of cheap % TODO urghs formulation
    %high-quality RGB-D sensors, it became possible to capture more and more
    %data not only as color images, but with additional depth information. The
    %depth channel provides important clues not only for scene structure, but
    %also for predicting semantic object classes.
    %We demonstrate how conditional random field learning, an approach
    %that has shown great promise for RGB images, can exploit depth information
    %to improve semantic interpretation of the scene.
    We evaluate our approach on the NYU V2 dataset of indoor scenes, a challenging
    dataset covering a wide variety of scene layouts and object classes. We
    hard-code much less information about the scene layout into our model then previous
    approaches, and instead learn object relations directly from the data. We
    find that our conditional random field approach improves upon previous
    work, setting a new state-of-the-art for the dataset.
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{INTRODUCTION}
For robots to perform varied tasks in unstructured environments, understanding their
sourroundings is essential. We formulate the problem of semantic annotation of maps
as a dense labeling of RGB-D images into semantic classes. Dense labeling of objects
and structure classes allows for a detailed reasoning about the scene.

In this work, we propose the use of random forests combined with conditional
random fields (CRFs) to perform robust estimation of structure classes in RGB-D
images. The CRF is learned using a structural support vector machine,
allowing it to integrate the noisy low-level information produced by a pixel-based
random forest to a consistent interpretation of the scene.

We thereby extend the success of learned conditional random field models for
semantic segmentation in RGB images to the domain of 3D scenes.
Our emphasis lies on expoiting the additional depth and 3D information in all
procsessing steps, while relying on \emph{learning} to create a model that 
is adjusted to the properties of the sensor input and environment.

Our approach starts with a random forest, providing a noisy local estimate
of semantic classes based on color and depth information. These estimates
are grouped together using a superpixel approach, for which we extend previous
superpixel algorithms from the RGB to the RGB-D domain.
We then build a geometric model of the scene, based on the neighborhood graph
of superpixels.  We use this graph not only to capture spacial relations in the
2d plane of the image, but also to model object distances and surface angles in
3d, using a point cloud generated from the RGB-D image.

We access the accuracy of our model on the challenging NYU Segmentation V2
dataset \citep{SilbermanECCV12}, where our model outperforms previous
approaches.  Our analysis shows that while our random forest model
already has competative performance, the superpixel-based grouping and in
pariculare the loss-based learning are integral ingredients of the success of our method.

\section{RELATED WORK}
The task of dense semantic labeling in natural images has been widely studied
in computer vision.  Our approach of using pixel-based low-level cues is
similar to the work of \citet{shotton2006textonboost}, who introduced
TextonBoost for semantic segmentation, and used a hand-coded CRF energy to
model spacial interactions. More recent work usually employ learned conditional
random fields, learning object interactions from the
data to directly maximize a loss function~\citep{lucchi2013learning, krahenbuhl2012efficient},
which is the approach we are following.

Work using RGB-D data only recently emmerged with
the availability of the NYU Depth Dataset V1~\citep{silberman2011indoor}.
\citet{silberman2011indoor} captured a wide variety of indoor scence using a structured light sensor,
and provided dense semantic object class annotation. Their work also introduced a baseline method
for semantic segmentation of RGB-D image, which used an approach based on superpixels, interest
point descriptors and a conditional random field. While pairwise potentials for the CRF were carfully
designed for the dataset, potentials were either directly set by hand or estimated using empirical
frequencies. This is in contrast to our work, which applies structured prediction techniques
to learn potentials automatically to optimize predictive performance.
\citet{ren2012rgb} focus on the design of features for semantic labeling of RGB-D data, and use
a hierarchical segmentation to provide context. While they also define a conditional random field on superpixels,
their model is again not learned, but a weighted potts model, using only a
probability of boundary map, and not taking spacial layout into account at all.

\citet{SilbermanECCV12} extendet the NYU Depth Dataset V1 to the NYU Depth Dataset V2 that we are also
using in this work.  Their focus is on inferring support relations in indoor
scence, such as objects resting on tables or shelfs, which in turn rest on the floor.
Their approach is based on robust estimation of 3D plane hypotheses, which are then jointly
optimized with support relations and structure classes.
\citet{SilbermanECCV12} use a complex pipeline, employing significant domain knowledge.
In this work, on the other hand, we try to learn all relevant domain specific features
directly from the data, which allows us to out-perform the work of \citet{SilbermanECCV12}
with respect to structure class segmentation.

\citet{couprie-iclr-13} approach the task of semantic segmentation of structure classes
in RGB-D using the paradigm of convolutional neural networks, extending
previous work of \citet{farabet-pami-13} and \citet{schulz2012learning}.
Similar to our approach, \citet{couprie-iclr-13} combine the output of a
pixel-based, low-level learning algorithm with an independent unsupervised
segmentation step. In contrast to their work, we improve our results by not
only averaging predictions within superpixels, but also explicitly learning
interactions between neighboring superpixels, favouring a consistent
interpretation of the whole image.

\citet{stueckler2013} proposed a real-time system for online learning and prediction of semantic classes.
Their main contribution is the online integration of low-level predictions over multiple frames
by estimating camera motion and building a 3D model of the scene.
We use the implementation of random forest provided by \citet{stueckler2013}, but instead of
integrating predictions over time, we focus on exploiting the structur within a single frame.

\section{LEARNING DEPTH-SENSITVE CONDITIONAL RANDOM FIELDS}
We take a conditional random field approach, whose nodes repesent a labeling of
superpixels.  We use an energy consisting of first and second order factors
(also called unary and pairwise potentials), with learned potential functions.
Let us denote the representation of an input image by $x$ and a labeling of
superpixels into semantic classes by $y$.  Then the general form of the energy is
\begin{equation}\eqlabel{energy}
    g(x, y) = \sum_{v \in V} \psi_v(x, y_v) + \sum_{(v, w) \in E} \psi_{v,w}(x, y_{v}, y_{w}).
\end{equation}
Here $V$ enumerates the superpixels, and $E\subset V \times V$ is a set of
edges, encoding neighborhood between superpixels.

We learn the unary and pairwise energy functions $\psi_v$ and $\psi_{v, w}$ from the training data
using a structural support vector machine. 
The concept of structural support vector machines allows for a principled,
maximum-margin based, loss-sensitive training of conditional random fields, that allows much
more complex interactions than the simple potts potentials that are often used in the literature.

In general, structural support vector machines learn the parameters $\theta$ of a predictor of the form
\begin{equation}\eqlabel{prediction}
f(x) = \argmax_{y \in \mathcal{Y}} \theta^T \Phi(x, y).
\end{equation}
We choose $\psi$ in \Eqref{energy} to be linear in the learnable parameters and
the data dependend features, resulting in a form equivalent to
\Eqref{prediction}. Our features are described in detail below.  We use the
$1$-lack formulation of the structural SVM~\citep{joachims2009cutting} and
solve the maximization in \Eqref{prediction} using a combination of fusion
moves~\citep{lempitsky2010fusion} and the AD$^3$ algorithm of
\citet{martins2011augmented}.  In contrast to graph-cut inference, fusion moves
and AD$^3$ can work with arbitrary potential function, and allow percise
learning using the structural support vector machine approach.

\subsection{Low Level Segmentation}
We take a super-pixel based approach to semantic segmentation.
Our superpixel generation is based on the SLIC algorithm~\citep{achanta2012slic}. We extend the
standard SLIC algorithm, which works on the Lab space to also include 
depth information. The resulting algorithm is a localized $k$-Means in Lab-D-XY space.
Our implementation is publicly available through the scikit-image library\footnote{\url{http://scikit-image.org}}.
Similar to \citet{SilbermanECCV12}, we found little visual improvement over the
RGB segmentation when using additional depth information. On the other hand,
estimation of per-superpixel features based on the 3D point cloud was more
robust when including depth information into the superpixel procedure.
%TODO visualize?
The resulting superpixels are compact in the 2D image. As the corresponding point
cloud is very sparse at depth jumps, it is unfortunately not possible to create
superpixels that are compact in 3D while maintaining a meaningful minimum size.

\begin{figure}
    \begin{center}
        \includegraphics[width=\linewidth]{images/height_success}\\
        \vspace{3mm}
        \includegraphics[width=\linewidth]{images/height_failure}
    \end{center}
    \caption{%
        Visualization of the height computed using the method described in \Secref{unaries}.
        Input images are shown on the left (depth not shown), the computed height is depicted on the right.
        The top row exemplifies a typical scene, while the bottom row shows a scene without horizontal
        surfaces, where our method fails.
    \figlabel{height}}
\end{figure}

\subsection{Unary Image Features}\seclabel{unaries}
Our method builds on the probability output of a random forest, trained for pixelwise
classification of the structure classes.
We use the GPU implementation provided by \citet{stueckler2013}.
The input for training are the full RGB-D images, transformed to Lab
color space. Each tree in the forest uses training pixel only from a subset of
training images. For each training image, an equal number of pixels for each
occurring class is sampled. Split features are given by difference of regions
on color or depth channels. Region size and offsets are normalized using the
depth at the target pixel.
We accumulate the probabilistic output for all pixels within a superpixel, and
use the resulting distribution as a feature for the unary node potentials in our CRF model.
We augment these prediction with another feature, based on the height of a superpixel in 3D.
This is a very informative feature, in particular to determin the floor.
To compute the height of a (super) pixel, we first find the ``up'' direction.
We use a very simple approach that we found effective: we cluster normal directions of all pixels
into 10 clusters using $k$-means, and use the one that is most parallel to the $Y$ direction, which
roughly corresponds to height in the dataset.
We then project the 3D pointcloud given by the depth along this direction, and normalize the result between
$0$ and $1$.
This procedure works robustly given there is any horizontal area in the image,
such as the ground or a table. A few scenes contain only walls and furniture,
and the approach fails for these. \Figref{height} illustrates a typical case and
one of the much rarer failure cases.
While we could use a more elaborat scheme,
such as the one from \citet{SilbermanECCV12}, we suspect that the feature is of
little use in scenes without horizontale surfaces.
\begin{figure}
    \begin{center}
        \includegraphics[width=\linewidth]{images/normal_feature}
    \end{center}
    \caption{%
        Visualization of one of the pairwise features, the similarity between superpixel normals.
        The image shows the zoom-in of a bedroom scene, together with the superpixel oversegmentation.
        Lines connect adjacent superpixels, and line-stregth gives the magnitude of the orientation similarity.
    \figlabel{normal_feature}}
\end{figure}

\subsection{Pairwise Depth-Sensitive Features}
There are five different features used to build pairwise potentials in our model:
\begin{description}
    \item[Constant] \hfill \\
        A constant feature allows to model general neighborhood relations.

    \item[Color Contrast] \hfill \\
        We employ a non-linear color contrast, as is common in the computer
        vision literature, between the superpixel mean colors $c_i$ and $c_j$:
        \[\exp\left(-\gamma \lVert c_i - c_j \rVert^2\right)\]

    \item[Vertical Alignment] \hfill \\
        We model the directed angle between superpixel centers in the 2d image
        plane.  This allows the  model to learn that ``structure'' is above
        ``floor'', but not the other way around.

    \item[Depth Difference] \hfill \\
        We include the signed depth difference between superpixels, which
        allows the model to detect depth discontinuities that are not
        represented in the 2d neighborhood graph of the superpixels.

    \item[Normal Orientations] \hfill \\
        Differences in normal vector orientation are a strong clue on
        whether two superpixels belong to the same surface, and therefore the
        same structural class.
        We compute the orientation of normals in the 3D using the method of \citet{holz_2011_robocup},
        as implemented in the point cloud library (pcl)\footnote{\url{http://pointclouds.org}}.
        All normals within a superpixel are then averaged, to get a single orientation for each superpixel.
        The feature is computed as $\frac{\pi}{4}$ minus the (undirected) angle between the normals belonging
        to two adjacent superpixels.  
        The feature is illustrated in \Figref{normal_feature}. The difference
        in normal orientation highlights that pillow and wall are distinct
        objects, even though there is no strong distinction in color or depth.
\end{description}

\section{EXPERIMENTS}

\begin{table*}[t]
\centering
\begin{tabularx}{\linewidth}{@{\extracolsep{\fill}}lcccccc}
\toprule
                        & ground        &  structure    & furniture     & props         & class average   & pixel average\\
\cmidrule(r){1-7}

RF                      &         90.8  &   81.6        & 67.9          & 19.9          &  65.0        &  68.3 \\
RF + SP                 &         92.5  &   83.3        & 73.8          & 13.9          &  65.7        &  70.1 \\ 
RF + SP + SVM           &         94.3  &   78.3        & 62.5          & \textbf{46.0} &  70.3        &  69.8 \\
RF + SP + CRF           &         94.8  &   78.7        &          70.8 & 41.6          &\textbf{71.5} &  \textbf{72.0} \\
\cmidrule(r){1-7}
\citet{SilbermanECCV12} &         68    &   59          & 70           & 42            &  59.6        & 58.6 \\
\citet{couprie-iclr-13} &         87.3  & \textbf{86.1} & 45.3         & 35.5          &  63.5        & 64.5 \\
\citet{stueckler2013}   & \textbf{95.6} &   83.0        & \textbf{75.1}& 14.2          &  67.0        & 70.9 \\

\bottomrule
\end{tabularx}
    \caption{Quantitative comparison of the proposed method with the
literature. The best value in each column is printed in bold. The upper part of
the table shows contributions by different parts of our pipeline. RF stands for random forest prediction, RF + SP for aggregated
random forests prediction within superpixels, RF + SP + SVM for an SVM trained on the unary potentials, and RF + SP + CRF is
our proposed pipeline. We optimized our approach for class average
accuracy.\tablabel{results}}
\end{table*}

We evaluate our approach on the public NYU depth V2 segmentation dataset of
indoor scenes.  The dataset comes with a detailed annotation of 1449 indoor
RGB-D images belonging to a wide variety of indoor scenes, categorized into 26
scene classes.  The annotation contains four semantic structural classes:
structure, floor, furniture and prop. There is an additional ``void'' class,
which is used for object boundaries and hard-to-annotate regions. We follow the
literature in excluding these pixels completely from the evaluation.
We optimize our model for \emph{average class accuracy} (the mean of the
diagonal of the confusion matrix), which puts more emphasis on the harder
classes of props and furniture, which have smaller area than structure and
floor.

Our approach is implemented using our \textsc{PyStruct}
library~\footnote{\url{http://pystruct.github.io}}.  The code for our
experiments will be released upon acceptance. We use \textsc{scikit-learn}~\citep{pedregosa2011scikit}
for $k$-means clustering and the SVM baseline.

All hyper parameters were adjusted using 5-fold cross-validation. The
hyper parameters of the random forests were found using the \texttt{hyperopt}
framework of \cite{bergstra2011algorithms}. For the CRF model, the only
hyper-parameters are related to the superpixel segmentation, and the single
hyper-parameter $C$ of the structural SVM formulation. These were adjusted
using standard grid-search.
We found 500 superpixels per image to work best, which allow for a maximum
performance of 95\% average class accuracy on the validation set.

\subsection{Results}
\Tabref{results} compares different components of our approach with the literature.
Please note that we \emph{first} designed our final model, using only the
validation data. We now report accuracies of simpler models for reference,
however these results were not used for model selection. To separate
the influence of loss-based training and the spacial reasoning of the conditional random field,
we also train a standard support vector machine on the unary potentials for comparison.

The random forest prediction, as reported in \citet{stueckler2013} is already quite competitive.
Grouping into superpixels slightly improves performance, by removing
high-frequency noise and snapping to object boundaries. Somewhat surprisingly,
using a standard unstructured SVM with rescaled loss already advances the mean
accuracy decidedly above the previous state-of-the art. We
attribute this mostly to the ability of the SVM to more directly minimize the
target loss, leading to a calibration for the actual error measure. On the
other hand, the total accuracy only decreases by $0.3\%$, while the average
accuracy increases by $4.5\%$. This means that the SVM can further exploit
uncertainty within superpixels and correlations between classes.
This performance is still improved upon, both in class average and pixel average performance
by the learned conditional random field approach, yielding the best published result
so far for both measures. The increase over the standard SVM is $1.2\%$ for class average accuracy
and $2.2\%$ for pixel average accuracy.

A visualization of the impact of each processing step can be found in
\Figref{comparison}, which shows prediction results on the test set.  The for
prediction methods correspond to the rows of \Tabref{results}.  The difference
between the SVM and CRF approaches are clearly visible, with the CRF producing
results that are very close to the ground truth in serveral complex scenes.

We found that our approach improves results most for scenes with a clear geometric structure,
which is not surprising. We see that evidence from the random forest is often very noisy, and biased
away from the ``props'' class. While the unstructured SVM can correct somewhat
for the class imbalance, it has no way to make larger areas consistent, which
the conditional random field can.
On the other hand, performance of the CRF deteriorates sligthly on very crowded
scenes with a mixture of small furniture and prop objects, as
can be seen in the two right-most images. In these scenes, depth information is
often noisy, and it is hard to make geometric statements on the superpixel
level. As the input from the random forest is also often of low quality for
crowded scenes, the conditional random field has little chance to recover.

\begin{figure}
    \begin{center}
        \includegraphics[width=.45\linewidth]{images/vertical_alignment}\vspace{1mm}
    \includegraphics[width=.45\linewidth]{images/depth_difference}
    \end{center}
    \caption{%
        Visualization of some of the learned potentials. The right potential is
        applied to relative depth between superpixels, the second on the
        feature encoding whether one superpixel is above the other in the
        image. See text for details.
    \figlabel{weights}}
\end{figure}

\Figref{weights} visualizes some learned potential functions.
Higher values correspond to favored configurations. One can see that the
vertical alignment potential expresses that the floor is much more likely to be below
other classes. It also encodes the fact that props
rest on furniture, but not the other way around.
The potential of the depth feature encodes, for example, that the ground
is usually behind the other classes, while furniture is in front of structures,
such as the wall.
Interestingly, the potential functions are not anti-symmetric, and forcing them to be so
degrates the results. This suggests that the direction of connecting edges, going from
the top left to the bottom right in the image, is also exploited by the potentials.

\begin{figure*}
    \begin{tabu} to \linewidth{@{}XXXXX@{}}
    \includegraphics[width=\linewidth]{images/00845_image.png}&%
    \includegraphics[width=\linewidth]{images/00781_image.png}&%
    \includegraphics[width=\linewidth]{images/01331_image.png}&%
    \includegraphics[width=\linewidth]{images/00118_image.png}&%
    \includegraphics[width=\linewidth]{images/01203_image.png}\\
    \multicolumn{5}{@{}c@{}}{Input Image}\\

    \includegraphics[width=\linewidth]{images/00845_pixel.png}&%
    \includegraphics[width=\linewidth]{images/00781_pixel.png}&%
    \includegraphics[width=\linewidth]{images/01331_pixel.png}&%
    \includegraphics[width=\linewidth]{images/00118_pixel.png}&%
    \includegraphics[width=\linewidth]{images/01203_pixel.png}\\
    \multicolumn{5}{@{}c@{}}{Random Forest Prediction}\\

    \includegraphics[width=\linewidth]{images/00845_sp.png}&%
    \includegraphics[width=\linewidth]{images/00781_sp.png}&%
    \includegraphics[width=\linewidth]{images/01331_sp.png}&%
    \includegraphics[width=\linewidth]{images/00118_sp.png}&%
    \includegraphics[width=\linewidth]{images/01203_sp.png}\\
    \multicolumn{5}{@{}c@{}}{Superpixel Voting}\\

    \includegraphics[width=\linewidth]{images/00845_svm.png}&%
    \includegraphics[width=\linewidth]{images/00781_svm.png}&%
    \includegraphics[width=\linewidth]{images/01331_svm.png}&%
    \includegraphics[width=\linewidth]{images/00118_svm.png}&%
    \includegraphics[width=\linewidth]{images/01203_svm.png}\\
    \multicolumn{5}{@{}c@{}}{Support Vector Machine on Superpixels}\\

    \includegraphics[width=\linewidth]{images/00845_ssvm.png}&%
    \includegraphics[width=\linewidth]{images/00781_ssvm.png}&%
    \includegraphics[width=\linewidth]{images/01331_ssvm.png}&%
    \includegraphics[width=\linewidth]{images/00118_ssvm.png}&%
    \includegraphics[width=\linewidth]{images/01203_ssvm.png}\\
    \multicolumn{5}{@{}c@{}}{Conditional Random Field on Superpixels}\\

    \includegraphics[width=\linewidth]{images/00845_gt.png}&%
    \includegraphics[width=\linewidth]{images/00781_gt.png}&%
    \includegraphics[width=\linewidth]{images/01331_gt.png}&%
    \includegraphics[width=\linewidth]{images/00118_gt.png}&%
    \includegraphics[width=\linewidth]{images/01203_gt.png}\\
    \multicolumn{5}{@{}c@{}}{Ground Truth}\\
    \multicolumn{5}{@{}c@{}}{
        \includegraphics[]{legend.pdf}
    }
    \end{tabu}
\caption{%
Qualitative evaluation of the conditional random field.
The first three images illustrate errors in the original prediction that can be corrected, while
the second two images illustrate failure modes. See the text for details. Pixels marked as void
are excluded from the evaluation.
\figlabel{comparison}}
\end{figure*}

\section{SUMMARY AND DISCUSSION}
We introduce a conditional random field formulation for semantic segmentation
of structure classes in RGB-D images. We base our model in the output of an efficient GPU implementation
of random forest, and model spacial neighborhood using a superpixel-based approach.
We combine color, depth and 3D orientation features into an energy function that is fully learned using 
 the structural support vector machine approach.  By explicitly modeling 3D
 relations in a fully learned framework, we improve the state-of-the art on the
 NYU V2 dataset for semantic annotation of structure classes.

While our approach allows modelling of spacial relations, these are limited to
local interactions. In future work, these interactions could be extended to
larger areas using latent variable models~\citep{dann2012pottics} or higher
order potentials~\citep{kohli2009robust}.
Another possible line of future work is to combine our approach with a more
task-specific one, directly including support plane assumptions into the model, as done by
\citet{SilbermanECCV12}.

While this work did not explicitly address real time application, the random
forest implementation that we build upon allows for real-time
processing~\citep{stueckler2013}. The SLIC superpixel algorithm can also be
implemented on GPU in real-time, as was demonstrated by \citep{ren2011gslic}, and similarly
the normal features we use also have
real-time capabilities~\citep{holz_2011_robocup}.
Finally, fusion move inference for our model is very efficient for our model,
opening up the possibility to implement our approach entirely in real time.

\printbibliography{}

\end{document}

### 2013-09-12 sample/root.tex
Merge branch 'master' of svn.ais.uni-bonn.de:u/amueller/icra_2014_nyu
git-svn-id: https://svn.ais.uni-bonn.de/svn/staff/publications/icra_2014_mueller_nyu@4357 b2511e17-9ac0-488b-bc21-1d6d82e5baa2

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%2345678901234567890123456789012345678901234567890123456789012345678901234567890
%        1         2         3         4         5         6         7         8

%\documentclass[letterpaper, 10 pt, conference]{ieeeconf}  % Comment this line out if you need a4paper

\documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4 paper

\IEEEoverridecommandlockouts                              % This command is only needed if 
                                                          % you want to use the \thanks command

\overrideIEEEmargins                                      % Needed to meet printer requirements.

% See the \addtolength command later in the file to balance the column lengths
% on the last page of the document

% The following packages can be found on http:\\www.ctan.org
\usepackage{graphics} % for pdf, bitmapped graphics files
%\usepackage{epsfig} % for postscript graphics files
%\usepackage{mathptmx} % assumes new font selection scheme installed
%\usepackage{times} % assumes new font selection scheme installed
\usepackage{amsmath} % assumes amsmath package installed
\usepackage{amssymb}  % assumes amsmath package installed

\title{\LARGE \bf
Preparation of Papers for IEEE Sponsored Conferences \& Symposia*
}

\author{Albert Author$^{1}$ and Bernard D. Researcher$^{2}$% <-this % stops a space
\thanks{*This work was not supported by any organization}% <-this % stops a space
\thanks{$^{1}$Albert Author is with Faculty of Electrical Engineering, Mathematics and Computer Science,
        University of Twente, 7500 AE Enschede, The Netherlands
        {\tt\small albert.author@papercept.net}}%
\thanks{$^{2}$Bernard D. Researcheris with the Department of Electrical Engineering, Wright State University,
        Dayton, OH 45435, USA
        {\tt\small b.d.researcher@ieee.org}}%
}

\begin{document}

\maketitle
\thispagestyle{empty}
\pagestyle{empty}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}

This electronic document is a ÒliveÓ template. The various components of your paper [title, text, heads, etc.] are already defined on the style sheet, as illustrated by the portions given in this document.

\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{INTRODUCTION}

This template provides authors with most of the formatting specifications needed for preparing electronic versions of their papers. All standard paper components have been specified for three reasons: (1) ease of use when formatting individual papers, (2) automatic compliance to electronic requirements that facilitate the concurrent or later production of electronic products, and (3) conformity of style throughout a conference proceedings. Margins, column widths, line spacing, and type styles are built-in; examples of the type styles are provided throughout this document and are identified in italic type, within parentheses, following the example. Some components, such as multi-leveled equations, graphics, and tables are not prescribed, although the various table text styles are provided. The formatter will need to create these components, incorporating the applicable criteria that follow.

\section{PROCEDURE FOR PAPER SUBMISSION}

\subsection{Selecting a Template (Heading 2)}

First, confirm that you have the correct template for your paper size. This template has been tailored for output on the US-letter paper size. 
It may be used for A4 paper size if the paper size setting is suitably modified.

\subsection{Maintaining the Integrity of the Specifications}

The template is used to format your paper and style the text. All margins, column widths, line spaces, and text fonts are prescribed; please do not alter them. You may note peculiarities. For example, the head margin in this template measures proportionately more than is customary. This measurement and others are deliberate, using specifications that anticipate your paper as one part of the entire proceedings, and not as an independent document. Please do not revise any of the current designations

\section{MATH}

Before you begin to format your paper, first write and save the content as a separate text file. Keep your text and graphic files separate until after the text has been formatted and styled. Do not use hard tabs, and limit use of hard returns to only one return at the end of a paragraph. Do not add any kind of pagination anywhere in the paper. Do not number text heads-the template will do that for you.

Finally, complete content and organizational editing before formatting. Please take note of the following items when proofreading spelling and grammar:

\subsection{Abbreviations and Acronyms} Define abbreviations and acronyms the first time they are used in the text, even after they have been defined in the abstract. Abbreviations such as IEEE, SI, MKS, CGS, sc, dc, and rms do not have to be defined. Do not use abbreviations in the title or heads unless they are unavoidable.

\subsection{Units}

\begin{itemize}

\item Use either SI (MKS) or CGS as primary units. (SI units are encouraged.) English units may be used as secondary units (in parentheses). An exception would be the use of English units as identifiers in trade, such as Ò3.5-inch disk driveÓ.
\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds. This often leads to confusion because equations do not balance dimensionally. If you must use mixed units, clearly state the units for each quantity that you use in an equation.
\item Do not mix complete spellings and abbreviations of units: ÒWb/m2Ó or Òwebers per square meterÓ, not Òwebers/m2Ó.  Spell out units when they appear in text: Ò. . . a few henriesÓ, not Ò. . . a few HÓ.
\item Use a zero before decimal points: Ò0.25Ó, not Ò.25Ó. Use Òcm3Ó, not ÒccÓ. (bullet list)

\end{itemize}

\subsection{Equations}

The equations are an exception to the prescribed specifications of this template. You will need to determine whether or not your equation should be typed using either the Times New Roman or the Symbol font (please no other font). To create multileveled equations, it may be necessary to treat the equation as a graphic and insert it into the text after your paper is styled. Number equations consecutively. Equation numbers, within parentheses, are to position flush right, as in (1), using a right tab stop. To make your equations more compact, you may use the solidus ( / ), the exp function, or appropriate exponents. Italicize Roman symbols for quantities and variables, but not Greek symbols. Use a long dash rather than a hyphen for a minus sign. Punctuate equations with commas or periods when they are part of a sentence, as in

$$
\alpha + \beta = \chi \eqno{(1)}
$$

Note that the equation is centered using a center tab stop. Be sure that the symbols in your equation have been defined before or immediately following the equation. Use Ò(1)Ó, not ÒEq. (1)Ó or Òequation (1)Ó, except at the beginning of a sentence: ÒEquation (1) is . . .Ó

\subsection{Some Common Mistakes}
\begin{itemize}

\item The word ÒdataÓ is plural, not singular.
\item The subscript for the permeability of vacuum ?0, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ÒoÓ.
\item In American English, commas, semi-/colons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation. When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks. A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this). (A parenthetical sentence is punctuated within the parentheses.)
\item A graph within a graph is an ÒinsetÓ, not an ÒinsertÓ. The word alternatively is preferred to the word ÒalternatelyÓ (unless you really mean something that alternates).
\item Do not use the word ÒessentiallyÓ to mean ÒapproximatelyÓ or ÒeffectivelyÓ.
\item In your paper title, if the words Òthat usesÓ can accurately replace the word ÒusingÓ, capitalize the ÒuÓ; if not, keep using lower-cased.
\item Be aware of the different meanings of the homophones ÒaffectÓ and ÒeffectÓ, ÒcomplementÓ and ÒcomplimentÓ, ÒdiscreetÓ and ÒdiscreteÓ, ÒprincipalÓ and ÒprincipleÓ.
\item Do not confuse ÒimplyÓ and ÒinferÓ.
\item The prefix ÒnonÓ is not a word; it should be joined to the word it modifies, usually without a hyphen.
\item There is no period after the ÒetÓ in the Latin abbreviation Òet al.Ó.
\item The abbreviation Òi.e.Ó means Òthat isÓ, and the abbreviation Òe.g.Ó means Òfor exampleÓ.

\end{itemize}

\section{USING THE TEMPLATE}

Use this sample document as your LaTeX source file to create your document. Save this file as {\bf root.tex}. You have to make sure to use the cls file that came with this distribution. If you use a different style file, you cannot expect to get required margins. Note also that when you are creating your out PDF file, the source file is only part of the equation. {\it Your \TeX\ $\rightarrow$ PDF filter determines the output file size. Even if you make all the specifications to output a letter file in the source - if your filter is set to produce A4, you will only get A4 output. }

It is impossible to account for all possible situation, one would encounter using \TeX. If you are using multiple \TeX\ files you must make sure that the ``MAIN`` source file is called root.tex - this is particularly important if your conference is using PaperPlaza's built in \TeX\ to PDF conversion tool.

\subsection{Headings, etc}

Text heads organize the topics on a relational, hierarchical basis. For example, the paper title is the primary text head because all subsequent material relates and elaborates on this one topic. If there are two or more sub-topics, the next level head (uppercase Roman numerals) should be used and, conversely, if there are not at least two sub-topics, then no subheads should be introduced. Styles named ÒHeading 1Ó, ÒHeading 2Ó, ÒHeading 3Ó, and ÒHeading 4Ó are prescribed.

\subsection{Figures and Tables}

Positioning Figures and Tables: Place figures and tables at the top and bottom of columns. Avoid placing them in the middle of columns. Large figures and tables may span across both columns. Figure captions should be below the figures; table heads should appear above the tables. Insert figures and tables after they are cited in the text. Use the abbreviation ÒFig. 1Ó, even at the beginning of a sentence.

\begin{table}[h]
\caption{An Example of a Table}
\label{table_example}
\begin{center}
\begin{tabular}{|c||c|}
\hline
One & Two\\
\hline
Three & Four\\
\hline
\end{tabular}
\end{center}
\end{table}

   \begin{figure}[thpb]
      \centering
      \framebox{\parbox{3in}{We suggest that you use a text box to insert a graphic (which is ideally a 300 dpi TIFF or EPS file, with all fonts embedded) because, in an document, this method is somewhat more stable than directly inserting a picture.
}}
      %\includegraphics[scale=1.0]{figurefile}
      \caption{Inductance of oscillation winding on amorphous
       magnetic core versus DC bias magnetic field}
      \label{figurelabel}
   \end{figure}

Figure Labels: Use 8 point Times New Roman for Figure labels. Use words rather than symbols or abbreviations when writing Figure axis labels to avoid confusing the reader. As an example, write the quantity ÒMagnetizationÓ, or ÒMagnetization, MÓ, not just ÒMÓ. If including units in the label, present them within parentheses. Do not label axes only with units. In the example, write ÒMagnetization (A/m)Ó or ÒMagnetization {A[m(1)]}Ó, not just ÒA/mÓ. Do not label axes with a ratio of quantities and units. For example, write ÒTemperature (K)Ó, not ÒTemperature/K.Ó

\section{CONCLUSIONS}

A conclusion section is not required. Although a conclusion may review the main points of the paper, do not replicate the abstract as the conclusion. A conclusion might elaborate on the importance of the work or suggest applications and extensions.

\addtolength{\textheight}{-12cm}   % This command serves to balance the column lengths
                                  % on the last page of the document manually. It shortens
                                  % the textheight of the last page by a suitable amount.
                                  % This command does not take effect until the next page
                                  % so it should come on the page before the last. Make
                                  % sure that you do not shorten the textheight too much.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{APPENDIX}

Appendixes should appear before the acknowledgment.

\section*{ACKNOWLEDGMENT}

The preferred spelling of the word ÒacknowledgmentÓ in America is without an ÒeÓ after the ÒgÓ. Avoid the stilted expression, ÒOne of us (R. B. G.) thanks . . .Ó  Instead, try ÒR. B. G. thanksÓ. Put sponsor acknowledgments in the unnumbered footnote on the first page.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

References are important to the reader; therefore, each citation must be complete and correct. If at all possible, references should be commonly available publications.

\begin{thebibliography}{99}

\bibitem{c1} G. O. Young, ÒSynthetic structure of industrial plastics (Book style with paper title and editor),Ó 	in Plastics, 2nd ed. vol. 3, J. Peters, Ed.  New York: McGraw-Hill, 1964, pp. 15Ð64.
\bibitem{c2} W.-K. Chen, Linear Networks and Systems (Book style).	Belmont, CA: Wadsworth, 1993, pp. 123Ð135.
\bibitem{c3} H. Poor, An Introduction to Signal Detection and Estimation.   New York: Springer-Verlag, 1985, ch. 4.
\bibitem{c4} B. Smith, ÒAn approach to graphs of linear forms (Unpublished work style),Ó unpublished.
\bibitem{c5} E. H. Miller, ÒA note on reflector arrays (Periodical styleÑAccepted for publication),Ó IEEE Trans. Antennas Propagat., to be publised.
\bibitem{c6} J. Wang, ÒFundamentals of erbium-doped fiber amplifiers arrays (Periodical styleÑSubmitted for publication),Ó IEEE J. Quantum Electron., submitted for publication.
\bibitem{c7} C. J. Kaufman, Rocky Mountain Research Lab., Boulder, CO, private communication, May 1995.
\bibitem{c8} Y. Yorozu, M. Hirano, K. Oka, and Y. Tagawa, ÒElectron spectroscopy studies on magneto-optical media and plastic substrate interfaces(Translation Journals style),Ó IEEE Transl. J. Magn.Jpn., vol. 2, Aug. 1987, pp. 740Ð741 [Dig. 9th Annu. Conf. Magnetics Japan, 1982, p. 301].
\bibitem{c9} M. Young, The Techincal Writers Handbook.  Mill Valley, CA: University Science, 1989.
\bibitem{c10} J. U. Duncombe, ÒInfrared navigationÑPart I: An assessment of feasibility (Periodical style),Ó IEEE Trans. Electron Devices, vol. ED-11, pp. 34Ð39, Jan. 1959.
\bibitem{c11} S. Chen, B. Mulgrew, and P. M. Grant, ÒA clustering technique for digital communications channel equalization using radial basis function networks,Ó IEEE Trans. Neural Networks, vol. 4, pp. 570Ð578, July 1993.
\bibitem{c12} R. W. Lucky, ÒAutomatic equalization for digital communication,Ó Bell Syst. Tech. J., vol. 44, no. 4, pp. 547Ð588, Apr. 1965.
\bibitem{c13} S. P. Bingulac, ÒOn the compatibility of adaptive controllers (Published Conference Proceedings style),Ó in Proc. 4th Annu. Allerton Conf. Circuits and Systems Theory, New York, 1994, pp. 8Ð16.
\bibitem{c14} G. R. Faulhaber, ÒDesign of service systems with priority reservation,Ó in Conf. Rec. 1995 IEEE Int. Conf. Communications, pp. 3Ð8.
\bibitem{c15} W. D. Doyle, ÒMagnetization reversal in films with biaxial anisotropy,Ó in 1987 Proc. INTERMAG Conf., pp. 2.2-1Ð2.2-6.
\bibitem{c16} G. W. Juette and L. E. Zeffanella, ÒRadio noise currents n short sections on bundle conductors (Presented Conference Paper style),Ó presented at the IEEE Summer power Meeting, Dallas, TX, June 22Ð27, 1990, Paper 90 SM 690-0 PWRS.
\bibitem{c17} J. G. Kreifeldt, ÒAn analysis of surface-detected EMG as an amplitude-modulated noise,Ó presented at the 1989 Int. Conf. Medicine and Biological Engineering, Chicago, IL.
\bibitem{c18} J. Williams, ÒNarrow-band analyzer (Thesis or Dissertation style),Ó Ph.D. dissertation, Dept. Elect. Eng., Harvard Univ., Cambridge, MA, 1993. 
\bibitem{c19} N. Kawasaki, ÒParametric study of thermal and chemical nonequilibrium nozzle flow,Ó M.S. thesis, Dept. Electron. Eng., Osaka Univ., Osaka, Japan, 1993.
\bibitem{c20} J. P. Wilkinson, ÒNonlinear resonant circuit devices (Patent style),Ó U.S. Patent 3 624 12, July 16, 1990.

\end{thebibliography}

\end{document}

### 2013-09-12 paper.tex
Spell checker.
git-svn-id: https://svn.ais.uni-bonn.de/svn/staff/publications/icra_2014_mueller_nyu@4360 b2511e17-9ac0-488b-bc21-1d6d82e5baa2

@@
     images. 
-    Our method learns to reason about spacial relations of objects and
+    Our method learns to reason about spatial relations of objects and
     fuses low-level class predictions to a consistent interpretation of a
-    scene. Our model incooporates color, depth and 3D scene features, on which
+    scene. Our model incorporates color, depth and 3D scene features, on which
     an energy function is learned to directly optimize object class prediction using
@@
 For robots to perform varied tasks in unstructured environments, understanding their
-sourroundings is essential. We formulate the problem of semantic annotation of maps
+surroundings is essential. We formulate the problem of semantic annotation of maps
 as a dense labeling of RGB-D images into semantic classes. Dense labeling of objects
@@
 semantic segmentation in RGB images to the domain of 3D scenes.
-Our emphasis lies on expoiting the additional depth and 3D information in all
-procsessing steps, while relying on \emph{learning} to create a model that 
+Our emphasis lies on exploiting the additional depth and 3D information in all
+processing steps, while relying on \emph{learning} to create a model that 
 is adjusted to the properties of the sensor input and environment.
@@
 approaches.  Our analysis shows that while our random forest model
-already has competative performance, the superpixel-based grouping and in
-pariculare the loss-based learning are integral ingredients of the success of our method.
+already has competitive performance, the superpixel-based grouping and in
+particular the loss-based learning are integral ingredients of the success of our method.
 
@@
 
-Work using RGB-D data only recently emmerged with
+Work using RGB-D data only recently emerged with
 the availability of the NYU Depth Dataset V1~\citep{silberman2011indoor}.
-\citet{silberman2011indoor} captured a wide variety of indoor scence using a structured light sensor,
+\citet{silberman2011indoor} captured a wide variety of indoor scene using a structured light sensor,
 and provided dense semantic object class annotation. Their work also introduced a baseline method
 for semantic segmentation of RGB-D image, which used an approach based on superpixels, interest
-point descriptors and a conditional random field. While pairwise potentials for the CRF were carfully
+point descriptors and a conditional random field. While pairwise potentials for the CRF were carefully
 designed for the dataset, potentials were either directly set by hand or estimated using empirical
@@
 a hierarchical segmentation to provide context. While they also define a conditional random field on superpixels,
-their model is again not learned, but a weighted potts model, using only a
+their model is again not learned, but a weighted Potts model, using only a
 probability of boundary map, and not taking spacial layout into account at all.
 
-\citet{SilbermanECCV12} extendet the NYU Depth Dataset V1 to the NYU Depth Dataset V2 that we are also
+\citet{SilbermanECCV12} extended the NYU Depth Dataset V1 to the NYU Depth Dataset V2 that we are also
 using in this work.  Their focus is on inferring support relations in indoor
-scence, such as objects resting on tables or shelfs, which in turn rest on the floor.
+scenes, such as objects resting on tables or shelfs, which in turn rest on the floor.
 Their approach is based on robust estimation of 3D plane hypotheses, which are then jointly
@@
 only averaging predictions within superpixels, but also explicitly learning
-interactions between neighboring superpixels, favouring a consistent
+interactions between neighboring superpixels, favoring a consistent
 interpretation of the whole image.
@@
 We use the implementation of random forest provided by \citet{stueckler2013}, but instead of
-integrating predictions over time, we focus on exploiting the structur within a single frame.
+integrating predictions over time, we focus on exploiting the structure within a single frame.
 
 \section{LEARNING DEPTH-SENSITVE CONDITIONAL RANDOM FIELDS}
-We take a conditional random field approach, whose nodes repesent a labeling of
+We take a conditional random field approach, whose nodes represent a labeling of
 superpixels.  We use an energy consisting of first and second order factors
@@
 maximum-margin based, loss-sensitive training of conditional random fields, that allows much
-more complex interactions than the simple potts potentials that are often used in the literature.
+more complex interactions than the simple Potts potentials that are often used in the literature.
 
@@
 We choose $\psi$ in \Eqref{energy} to be linear in the learnable parameters and
-the data dependend features, resulting in a form equivalent to
+the data-depended features, resulting in a form equivalent to
 \Eqref{prediction}. Our features are described in detail below.  We use the
@@
 \citet{martins2011augmented}.  In contrast to graph-cut inference, fusion moves
-and AD$^3$ can work with arbitrary potential function, and allow percise
+and AD$^3$ can work with arbitrary potential function, and allow precise
 learning using the structural support vector machine approach.
@@
 \subsection{Unary Image Features}\seclabel{unaries}
-Our method builds on the probability output of a random forest, trained for pixelwise
+Our method builds on the probability output of a random forest, trained for pixel-wise
 classification of the structure classes.
@@
 We augment these prediction with another feature, based on the height of a superpixel in 3D.
-This is a very informative feature, in particular to determin the floor.
+This is a very informative feature, in particular to determine the floor.
 To compute the height of a (super) pixel, we first find the ``up'' direction.
@@
 roughly corresponds to height in the dataset.
-We then project the 3D pointcloud given by the depth along this direction, and normalize the result between
+We then project the 3D point cloud given by the depth along this direction, and normalize the result between
 $0$ and $1$.
@@
 one of the much rarer failure cases.
-While we could use a more elaborat scheme,
+While we could use a more elaborate scheme,
 such as the one from \citet{SilbermanECCV12}, we suspect that the feature is of
-little use in scenes without horizontale surfaces.
+little use in scenes without horizontal surfaces.
 \begin{figure}
@@
         The image shows the zoom-in of a bedroom scene, together with the superpixel oversegmentation.
-        Lines connect adjacent superpixels, and line-stregth gives the magnitude of the orientation similarity.
+        Lines connect adjacent superpixels, and line-strength gives the magnitude of the orientation similarity.
     \figlabel{normal_feature}}
@@
 between the SVM and CRF approaches are clearly visible, with the CRF producing
-results that are very close to the ground truth in serveral complex scenes.
+results that are very close to the ground truth in several complex scenes.
 
@@
 the conditional random field can.
-On the other hand, performance of the CRF deteriorates sligthly on very crowded
+On the other hand, performance of the CRF deteriorates slightly on very crowded
 scenes with a mixture of small furniture and prop objects, as
@@
 Interestingly, the potential functions are not anti-symmetric, and forcing them to be so
-degrates the results. This suggests that the direction of connecting edges, going from
+degrades the results. This suggests that the direction of connecting edges, going from
 the top left to the bottom right in the image, is also exploited by the potentials.
@@
 
-While our approach allows modelling of spacial relations, these are limited to
+While our approach allows modeling of spacial relations, these are limited to
 local interactions. In future work, these interactions could be extended to

### 2013-09-13 paper.tex
include some remarks, add refstyle for \secref withouth paragraph symbol.
git-svn-id: https://svn.ais.uni-bonn.de/svn/staff/publications/icra_2014_mueller_nyu@4367 b2511e17-9ac0-488b-bc21-1d6d82e5baa2

@@
 We then build a geometric model of the scene, based on the neighborhood graph
-of superpixels.  We use this graph not only to capture spacial relations in the
-2d plane of the image, but also to model object distances and surface angles in
-3d, using a point cloud generated from the RGB-D image.
+of superpixels.  We use this graph not only to capture spatial relations in the
+2D plane of the image, but also to model object distances and surface angles in
+3D, using a point cloud generated from the RGB-D image.
 
-We access the accuracy of our model on the challenging NYU Segmentation V2
+We assess the accuracy of our model on the challenging NYU Segmentation V2
 dataset \citep{SilbermanECCV12}, where our model outperforms previous
@@
 TextonBoost for semantic segmentation, and used a hand-coded CRF energy to
-model spacial interactions. More recent work usually employ learned conditional
+model spatial interactions. More recent work usually employ learned conditional
 random fields, learning object interactions from the
@@
 the availability of the NYU Depth Dataset V1~\citep{silberman2011indoor}.
-\citet{silberman2011indoor} captured a wide variety of indoor scene using a structured light sensor,
+\citet{silberman2011indoor} captured a wide variety of indoor scenes using a structured light sensor,
 and provided dense semantic object class annotation. Their work also introduced a baseline method
@@
 their model is again not learned, but a weighted Potts model, using only a
-probability of boundary map, and not taking spacial layout into account at all.
+probability of boundary map, and not taking spatial layout into account at all.
 
@@
 We learn the unary and pairwise energy functions $\psi_v$ and $\psi_{v, w}$ from the training data
-using a structural support vector machine. 
+using a structural support vector machine~\citep{joachims2009cutting}. 
 The concept of structural support vector machines allows for a principled,
-maximum-margin based, loss-sensitive training of conditional random fields, that allows much
+maximum-margin based, loss-sensitive training of conditional random fields. Learning the potential yields much
 more complex interactions than the simple Potts potentials that are often used in the literature.
@@
 classification of the structure classes.
-We use the GPU implementation provided by \citet{stueckler2013}.
+We use the GPU implementation provided by \citet{stueckler2013}\footnote{\url{https://github.com/deeplearningais/curfil}}.
 The input for training are the full RGB-D images, transformed to Lab
-color space. Each tree in the forest uses training pixel only from a subset of
+color space. Each tree in the forest uses training pixels only from a subset of
 training images. For each training image, an equal number of pixels for each
@@
         Visualization of one of the pairwise features, the similarity between superpixel normals.
-        The image shows the zoom-in of a bedroom scene, together with the superpixel oversegmentation.
+        The image shows the zoom-in of a bedroom scene, together with the superpixel over-segmentation.
         Lines connect adjacent superpixels, and line-strength gives the magnitude of the orientation similarity.
@@
         vision literature, between the superpixel mean colors $c_i$ and $c_j$:
-        \[\exp\left(-\gamma \lVert c_i - c_j \rVert^2\right)\]
+        \[\exp\left(-\gamma \lVert c_i - c_j \rVert^2\right).\]
 
     \item[Vertical Alignment] \hfill \\
-        We model the directed angle between superpixel centers in the 2d image
+        We model the directed angle between superpixel centers in the 2D image
         plane.  This allows the  model to learn that ``structure'' is above
@@
         allows the model to detect depth discontinuities that are not
-        represented in the 2d neighborhood graph of the superpixels.
+        represented in the 2D neighborhood graph of the superpixels.
 
@@
         same structural class.
-        We compute the orientation of normals in the 3D using the method of \citet{holz_2011_robocup},
+        We compute the 3D orientation of normals using the method of \citet{holz_2011_robocup},
         as implemented in the point cloud library (pcl)\footnote{\url{http://pointclouds.org}}.
@@
 however these results were not used for model selection. To separate
-the influence of loss-based training and the spacial reasoning of the conditional random field,
+the influence of loss-based training and the spatial reasoning of the conditional random field,
 we also train a standard support vector machine on the unary potentials for comparison.
@@
 target loss, leading to a calibration for the actual error measure. On the
-other hand, the total accuracy only decreases by $0.3\%$, while the average
+other hand, the average pixel accuracy only decreases by $0.3\%$, while the average class
 accuracy increases by $4.5\%$. This means that the SVM can further exploit
@@
 A visualization of the impact of each processing step can be found in
-\Figref{comparison}, which shows prediction results on the test set.  The for
+\Figref{comparison}, which shows prediction results on the test set.  The four
 prediction methods correspond to the rows of \Tabref{results}.  The difference
@@
 of structure classes in RGB-D images. We base our model in the output of an efficient GPU implementation
-of random forest, and model spacial neighborhood using a superpixel-based approach.
+of random forest, and model spatial neighborhood using a superpixel-based approach.
 We combine color, depth and 3D orientation features into an energy function that is fully learned using 
@@
 
-While our approach allows modeling of spacial relations, these are limited to
+While our approach allows modeling of spatial relations, these are limited to
 local interactions. In future work, these interactions could be extended to

### 2013-09-13 paper.tex
hacking around the legend and spacing, changing results to the ones with height features and change text accordingly.
git-svn-id: https://svn.ais.uni-bonn.de/svn/staff/publications/icra_2014_mueller_nyu@4368 b2511e17-9ac0-488b-bc21-1d6d82e5baa2

@@
 
-\section{EXPERIMENTS}
+\section{EXPERIMENTS}\seclabel{experiments}
 
@@
 RF + SP                 &         92.5  &   83.3        & 73.8          & 13.9          &  65.7        &  70.1 \\ 
-RF + SP + SVM           &         94.3  &   78.3        & 62.5          & \textbf{46.0} &  70.3        &  69.8 \\
-RF + SP + CRF           &         94.8  &   78.7        &          70.8 & 41.6          &\textbf{71.5} &  \textbf{72.0} \\
+RF + SP + SVM           &         94.4  &   79.1        & 64.2          & \textbf{44.0} &  70.4        &  70.3 \\
+RF + SP + CRF           &         94.9  &   78.9        &          71.1 & 42.7          &\textbf{71.9} &  \textbf{72.3} \\
 \cmidrule(r){1-7}
@@
 
-\subsection{Results}
+\subsection{Results}\seclabel{results}
 \Tabref{results} compares different components of our approach with the literature.
@@
 accuracy decidedly above the previous state-of-the art. We
-attribute this mostly to the ability of the SVM to more directly minimize the
-target loss, leading to a calibration for the actual error measure. On the
-other hand, the average pixel accuracy only decreases by $0.3\%$, while the average class
-accuracy increases by $4.5\%$. This means that the SVM can further exploit
-uncertainty within superpixels and correlations between classes.
-This performance is still improved upon, both in class average and pixel average performance
-by the learned conditional random field approach, yielding the best published result
-so far for both measures. The increase over the standard SVM is $1.2\%$ for class average accuracy
-and $2.2\%$ for pixel average accuracy.
+attribute this mostly to the ability of the SVM to exploit correlation between
+classes and uncertainty within the superpixels.
+Additionally, the SVM has access to the ``height'' feature, that was not
+included in the random forest.
+This performance is still improved upon, both in class average and pixel
+average performance by the learned conditional random field approach, yielding
+the best published result so far for both measures. The increase over the
+standard SVM is $1.5\%$ for class average accuracy and $2.0\%$ for pixel
+average accuracy.
 
@@
         feature encoding whether one superpixel is above the other in the
-        image. See text for details.
+        image. See \secref{results} for details.
     \figlabel{weights}}
@@
     \includegraphics[width=\linewidth]{images/01203_image.png}\\
-    \multicolumn{5}{@{}c@{}}{Input Image}\\
+    \multicolumn{5}{@{}c@{}}{Input Image}\vspace{3mm}\\
 
@@
     \includegraphics[width=\linewidth]{images/01203_pixel.png}\\
-    \multicolumn{5}{@{}c@{}}{Random Forest Prediction}\\
+    \multicolumn{5}{@{}c@{}}{Random Forest Prediction}\vspace{3mm}\\
 
@@
     \includegraphics[width=\linewidth]{images/01203_sp.png}\\
-    \multicolumn{5}{@{}c@{}}{Superpixel Voting}\\
+    \multicolumn{5}{@{}c@{}}{Superpixel Voting}\vspace{3mm}\\
 
@@
     \includegraphics[width=\linewidth]{images/01203_svm.png}\\
-    \multicolumn{5}{@{}c@{}}{Support Vector Machine on Superpixels}\\
+    \multicolumn{5}{@{}c@{}}{Support Vector Machine on Superpixels}\vspace{3mm}\\
 
@@
     \includegraphics[width=\linewidth]{images/01203_ssvm.png}\\
-    \multicolumn{5}{@{}c@{}}{Conditional Random Field on Superpixels}\\
+    \multicolumn{5}{@{}c@{}}{Conditional Random Field on Superpixels}\vspace{3mm}\\
 
@@
     \includegraphics[width=\linewidth]{images/01203_gt.png}\\
-    \multicolumn{5}{@{}c@{}}{Ground Truth}\\
+    \multicolumn{5}{@{}c@{}}{Ground Truth}\vspace{3mm}\\
     \multicolumn{5}{@{}c@{}}{
@@
 The first three images illustrate errors in the original prediction that can be corrected, while
-the second two images illustrate failure modes. See the text for details. Pixels marked as void
-are excluded from the evaluation.
+the second two images illustrate failure modes. Pixels marked as void
+are excluded from the evaluation. See the \secref{results} for details.
 \figlabel{comparison}}
@@
 Another possible line of future work is to combine our approach with a more
-task-specific one, directly including support plane assumptions into the model, as done by
-\citet{SilbermanECCV12}.
+task-specific one, directly including support plane assumptions into the model,
+as done by \citet{SilbermanECCV12}. Finally, we could also combine our
+single-frame approach with the approach of \citet{stueckler2013}, which fuses
+individual views in 3D to exploit temporal coherence.
 

### 2013-09-13 paper.tex
remarks hannes
git-svn-id: https://svn.ais.uni-bonn.de/svn/staff/publications/icra_2014_mueller_nyu@4369 b2511e17-9ac0-488b-bc21-1d6d82e5baa2

@@
 %\usepackage[numbers]{natbib}
-\usepackage[natbib, style=ieee]{biblatex}
+\usepackage[natbib, style=ieee,minnames=1, maxcitenames=2,sorting=none]{biblatex}
 \addbibresource{paper.bib}
@@
 
-Work using RGB-D data only recently emerged with
+Work semantic segmentation and mapping using RGB-D data only recently emerged with
 the availability of the NYU Depth Dataset V1~\citep{silberman2011indoor}.
@@
 Here $V$ enumerates the superpixels, and $E\subset V \times V$ is a set of
-edges, encoding neighborhood between superpixels.
+edges, encoding adjacence between superpixels.
 
@@
 \Eqref{prediction}. Our features are described in detail below.  We use the
-$1$-lack formulation of the structural SVM~\citep{joachims2009cutting} and
+$1$-slack formulation of the structural SVM~\citep{joachims2009cutting} and
 solve the maximization in \Eqref{prediction} using a combination of fusion
@@
 Our superpixel generation is based on the SLIC algorithm~\citep{achanta2012slic}. We extend the
-standard SLIC algorithm, which works on the Lab space to also include 
+standard SLIC algorithm, which works on the Lab space, to also include 
 depth information. The resulting algorithm is a localized $k$-Means in Lab-D-XY space.
@@
 To compute the height of a (super) pixel, we first find the ``up'' direction.
-We use a very simple approach that we found effective: we cluster normal directions of all pixels
-into 10 clusters using $k$-means, and use the one that is most parallel to the $Y$ direction, which
-roughly corresponds to height in the dataset.
-We then project the 3D point cloud given by the depth along this direction, and normalize the result between
-$0$ and $1$.
-This procedure works robustly given there is any horizontal area in the image,
+We use a very simple approach that we found effective: we cluster normal
+directions of all pixels into 10 clusters using $k$-means, and use the one that
+is most parallel to the $Y$ direction, which roughly corresponds to height in
+the dataset.
+We then project the 3D point cloud given by the depth along this direction, and
+normalize the result between $0$ and $1$.
+This procedure works robustly given there is some horizontal surface in the image,
 such as the ground or a table. A few scenes contain only walls and furniture,
@@
 There are five different features used to build pairwise potentials in our model:
-\begin{description}
-    \item[Constant] \hfill \\
+
+\emph{Constant}
     A constant feature allows to model general neighborhood relations.
 
-    \item[Color Contrast] \hfill \\
+\emph{Color Contrast}
     We employ a non-linear color contrast, as is common in the computer
@@
 
-    \item[Vertical Alignment] \hfill \\
+\emph{Vertical Alignment}
     We model the directed angle between superpixel centers in the 2D image
@@
 
-    \item[Depth Difference] \hfill \\
+\emph{Depth Difference}
     We include the signed depth difference between superpixels, which
@@
 
-    \item[Normal Orientations] \hfill \\
+\emph{Normal Orientations}
     Differences in normal vector orientation are a strong clue on
@@
     All normals within a superpixel are then averaged, to get a single orientation for each superpixel.
-        The feature is computed as $\frac{\pi}{4}$ minus the (undirected) angle between the normals belonging
+    The feature is computed as the difference of $\frac{\pi}{4}$ and the (undirected) angle between the normals belonging
     to two adjacent superpixels.  
-        The feature is illustrated in \Figref{normal_feature}. The difference
+    The feature is illustrated in \Figref{normal_feature}. The change
     in normal orientation highlights that pillow and wall are distinct
     objects, even though there is no strong distinction in color or depth.
-\end{description}
 
@@
 Our approach is implemented using our \textsc{PyStruct}
-library~\footnote{\url{http://pystruct.github.io}}.  The code for our
+library\footnote{\url{http://pystruct.github.io}}.  The code for our
 experiments will be released upon acceptance. We use \textsc{scikit-learn}~\citep{pedregosa2011scikit}
@@
 We found 500 superpixels per image to work best, which allow for a maximum
-performance of 95\% average class accuracy on the validation set.
+possible performance of 95\% average class accuracy on the validation set.
 

### 2013-09-13 paper.tex
fix plots, add teaser
git-svn-id: https://svn.ais.uni-bonn.de/svn/staff/publications/icra_2014_mueller_nyu@4372 b2511e17-9ac0-488b-bc21-1d6d82e5baa2

@@
 2D plane of the image, but also to model object distances and surface angles in
-3D, using a point cloud generated from the RGB-D image.
+3D, using a point cloud generated from the RGB-D image. The process is depicted
+in \Figref{teaser}.
 
@@
 particular the loss-based learning are integral ingredients of the success of our method.
+
+\begin{figure}
+    \begin{center}
+        \includegraphics[width=\linewidth]{images/teaser}
+    \end{center}
+    \caption{%
+        Visualization of the method proposed in this paper see \Secref{learning} for details.\label{teaser}
+    \figlabel{height}}
+\end{figure}
 
@@
 
-\section{LEARNING DEPTH-SENSITVE CONDITIONAL RANDOM FIELDS}
+\section{LEARNING DEPTH-SENSITVE CONDITIONAL RANDOM FIELDS}\seclabel{learning}
 We take a conditional random field approach, whose nodes represent a labeling of
@@
 
-\subsection{Low Level Segmentation}
-We take a super-pixel based approach to semantic segmentation.
-Our superpixel generation is based on the SLIC algorithm~\citep{achanta2012slic}. We extend the
-standard SLIC algorithm, which works on the Lab space, to also include 
-depth information. The resulting algorithm is a localized $k$-Means in Lab-D-XY space.
-Our implementation is publicly available through the scikit-image library\footnote{\url{http://scikit-image.org}}.
-Similar to \citet{SilbermanECCV12}, we found little visual improvement over the
-RGB segmentation when using additional depth information. On the other hand,
-estimation of per-superpixel features based on the 3D point cloud was more
-robust when including depth information into the superpixel procedure.
-%TODO visualize?
-The resulting superpixels are compact in the 2D image. As the corresponding point
-cloud is very sparse at depth jumps, it is unfortunately not possible to create
-superpixels that are compact in 3D while maintaining a meaningful minimum size.
-
 \begin{figure}
@@
 \end{figure}
+
+\subsection{Low Level Segmentation}
+We take a super-pixel based approach to semantic segmentation.
+Our superpixel generation is based on the SLIC algorithm~\citep{achanta2012slic}. We extend the
+standard SLIC algorithm, which works on the Lab space, to also include 
+depth information. The resulting algorithm is a localized $k$-Means in Lab-D-XY space.
+Our implementation is publicly available through the scikit-image library\footnote{\url{http://scikit-image.org}}.
+Similar to \citet{SilbermanECCV12}, we found little visual improvement over the
+RGB segmentation when using additional depth information. On the other hand,
+estimation of per-superpixel features based on the 3D point cloud was more
+robust when including depth information into the superpixel procedure.
+%TODO visualize?
+The resulting superpixels are compact in the 2D image. As the density of the
+corresponding point cloud is dependent on the depth, we did not succeed in
+creating superpixels that are compact in 3D while maintaining a meaningful
+minimum size.
 

### 2013-09-13 paper.tex
Fix table caption
git-svn-id: https://svn.ais.uni-bonn.de/svn/staff/publications/icra_2014_mueller_nyu@4373 b2511e17-9ac0-488b-bc21-1d6d82e5baa2

@@
 \begin{table*}[t]
-\centering
+    \caption{Quantitative comparison of the proposed method with the
+    literature.\tablabel{results}}
 \begin{tabularx}{\linewidth}{@{\extracolsep{\fill}}lcccccc}
@@
 \end{tabularx}
-    \caption{Quantitative comparison of the proposed method with the
-literature. The best value in each column is printed in bold. The upper part of
+\quad\\The best value in each column is printed in bold. The upper part of
 the table shows contributions by different parts of our pipeline. RF stands for random forest prediction, RF + SP for aggregated
@@
 our proposed pipeline. We optimized our approach for class average
-accuracy.\tablabel{results}}
+accuracy.
 \end{table*}

### 2013-09-13 paper.tex
add a star (aka dagger) to the stueckler at al result.
git-svn-id: https://svn.ais.uni-bonn.de/svn/staff/publications/icra_2014_mueller_nyu@4374 b2511e17-9ac0-488b-bc21-1d6d82e5baa2

@@
 RF                              &         90.8  &   81.6        & 67.9          & 19.9          &  65.0        &  68.3 \\
-RF + SP                 &         92.5  &   83.3        & 73.8          & 13.9          &  65.7        &  70.1 \\ 
+RF + SP                         &         92.5  &   83.3        & \textbf{73.8} & 13.9          &  65.7        &  70.1 \\ 
 RF + SP + SVM                   &         94.4  &   79.1        & 64.2          & \textbf{44.0} &  70.4        &  70.3 \\
-RF + SP + CRF           &         94.9  &   78.9        &          71.1 & 42.7          &\textbf{71.9} &  \textbf{72.3} \\
+RF + SP + CRF                   & \textbf{94.9} &   78.9        &          71.1 & 42.7          &\textbf{71.9} &  \textbf{72.3} \\
 \cmidrule(r){1-7}
@@
 \citet{couprie-iclr-13}         &         87.3  & \textbf{86.1} & 45.3         & 35.5          &  63.5        & 64.5 \\
-\citet{stueckler2013}   & \textbf{95.6} &   83.0        & \textbf{75.1}& 14.2          &  67.0        & 70.9 \\
+\cmidrule(r){1-7}
+\citet{stueckler2013}$^\dagger$ & \textbf{95.6} &   83.0        & \textbf{75.1}& 14.2          &  67.0        & 70.9 \\
 
@@
 \end{tabularx}
-\quad\\The best value in each column is printed in bold. The upper part of
+\quad\\The best value in each column is printed in bold$^\dagger$. The upper part of
 the table shows contributions by different parts of our pipeline. RF stands for random forest prediction, RF + SP for aggregated
@@
 our proposed pipeline. We optimized our approach for class average
-accuracy.
+accuracy.\\
+$^\dagger$ \footnotesize Note that the work of \citet{stueckler2013} is not directly
+comparable, as they integrated information over multiple frames, and did not
+measure accuracy for pixels without valid depth measurement.
 \end{table*}

### 2013-09-14 paper.tex
Bildunterschrift, rote Kringel.
git-svn-id: https://svn.ais.uni-bonn.de/svn/staff/publications/icra_2014_mueller_nyu@4375 b2511e17-9ac0-488b-bc21-1d6d82e5baa2
redo related work, criple citations.
git-svn-id: https://svn.ais.uni-bonn.de/svn/staff/publications/icra_2014_mueller_nyu@4378 b2511e17-9ac0-488b-bc21-1d6d82e5baa2

@@
     %also for predicting semantic object classes.
-    %We demonstrate how conditional random field learning, an approach
+    %We demonstrate how CRF learning, an approach
     %that has shown great promise for RGB images, can exploit depth information
@@
 
-We thereby extend the success of learned conditional random field models for
+We thereby extend the success of learned CRF models for
 semantic segmentation in RGB images to the domain of 3D scenes.
@@
     \caption{%
-        Visualization of the method proposed in this paper see \Secref{learning} for details.\label{teaser}
+        Overview of the proposed semantic segmentation method.\label{teaser}
     \figlabel{height}}
@@
 \section{RELATED WORK}
-The task of dense semantic labeling in natural images has been widely studied
-in computer vision.  Our approach of using pixel-based low-level cues is
-similar to the work of \citet{shotton2006textonboost}, who introduced
-TextonBoost for semantic segmentation, and used a hand-coded CRF energy to
-model spatial interactions. More recent work usually employ learned conditional
-random fields, learning object interactions from the
-data to directly maximize a loss function~\citep{lucchi2013learning, krahenbuhl2012efficient},
-which is the approach we are following.
+The task of dense semantic annotation of 3D maps has seen an increased interest
+in recent years.  Early work includes \citet{nuchter2008towards}, who combine
+6D SLAM, surface annotation and object recognition, to build semantically
+annotated maps. They demonstrate their approach on a mobile robot in an indoor
+environment.
+%
+More recently \citet{sengupta2012automatic} introduced a dataset of
+semantically annotated street-scenes in a closed track, captured as pairs of
+stereo images. They approach the task by jointly reasoning about 3D layout and
+semantic of the scenes and produce a dense labeling on image level.  In
+\citet{senguptaurban}, they extend their approach to produce a volumetric
+reconstruction of the scene, together with a dense semantic labeling of the
+volumetric representation. Their approach to image segmentation is build on
+the hierarchical CRF apporach of
+\citet{ladicky2009associative}, which is similar in spirit to our approach,
+but uses Potts potentials together with cross-validation to set potentials.
 
-Work semantic segmentation and mapping using RGB-D data only recently emerged with
-the availability of the NYU Depth Dataset V1~\citep{silberman2011indoor}.
-\citet{silberman2011indoor} captured a wide variety of indoor scenes using a structured light sensor,
-and provided dense semantic object class annotation. Their work also introduced a baseline method
-for semantic segmentation of RGB-D image, which used an approach based on superpixels, interest
-point descriptors and a conditional random field. While pairwise potentials for the CRF were carefully
+Recent approaches for indoor semantic annotation of maps mostly focused on
+RGB-D images, which are now easy to obtain using structured light sensors.
+\citet{stuckler2012semantic} used a Random Forest model to obtain a dense
+semantic labeling of images, integrating predictions over multiple views in 3D.
+They evaluated their approach on a limited set of table-top and indoors scenes.
+%
+\citep{silberman2011indoor} introduced the NYU Depth Dataset V1 indoor dataset,
+which consisted of a large variety of densely annotated indoor scences, captured as RGB-D images.
+Their work also introduced a baseline method for semantic segmentation of RGB-D
+image, which used an approach based on superpixels, interest point descriptors
+and a CRF.
+While pairwise potentials for the CRF were carefully
 designed for the dataset, potentials were either directly set by hand or estimated using empirical
@@
 to learn potentials automatically to optimize predictive performance.
-\citet{ren2012rgb} focus on the design of features for semantic labeling of RGB-D data, and use
-a hierarchical segmentation to provide context. While they also define a conditional random field on superpixels,
+%
+\citet{ren2012rgb} evaluated the design of features for semantic labeling of RGB-D data, and use
+a hierarchical segmentation to provide context. While they also define a CRF on superpixels,
 their model is again not learned, but a weighted Potts model, using only a
 probability of boundary map, and not taking spatial layout into account at all.
-
+%
 \citet{SilbermanECCV12} extended the NYU Depth Dataset V1 to the NYU Depth Dataset V2 that we are also
@@
 
-\citet{stueckler2013} proposed a real-time system for online learning and prediction of semantic classes.
-Their main contribution is the online integration of low-level predictions over multiple frames
-by estimating camera motion and building a 3D model of the scene.
-We use the implementation of random forest provided by \citet{stueckler2013}, but instead of
-integrating predictions over time, we focus on exploiting the structure within a single frame.
+\citet{stueckler2013} extends the approach of \citet{stuckler2012semantic} to
+a real-time system for online learning and prediction of semantic classes. Their
+use a GPU implementation of random forests, and integrate 3D scene information
+in an online fashion. They evaluate their approach on the dataset of
+\citet{SilbermanECCV12} with promising results.
+We use the implementation of random forest provided by
+\citet{stueckler2013}, but instead of integrating predictions over time, we
+focus on exploiting the structure within a single frame.
+
+While many of the works mentioned in this chapter make use of a CRF
+approach, we are not aware of any prior work on semantic annotation of 3D maps
+that fully learns their potentials. This allows our approach to infer
+the scene structure from the data, without the need to specify relevant relations
+by hand.
+%The task of dense semantic labeling in natural images has been widely studied
+%in computer vision.  Our approach of using pixel-based low-level cues is
+%similar to the work of \citet{shotton2006textonboost}, who introduced
+%TextonBoost for semantic segmentation, and used a hand-coded CRF energy to
+%model spatial interactions. More recent work usually employ learned conditional
+%random fields, learning object interactions from the
+%data to directly maximize a loss function~\citep{lucchi2013learning, krahenbuhl2012efficient},
+%which is the approach we are following.
 
 \section{LEARNING DEPTH-SENSITVE CONDITIONAL RANDOM FIELDS}\seclabel{learning}
-We take a conditional random field approach, whose nodes represent a labeling of
+We take a CRF approach, whose nodes represent a labeling of
 superpixels.  We use an energy consisting of first and second order factors
@@
 We learn the unary and pairwise energy functions $\psi_v$ and $\psi_{v, w}$ from the training data
-using a structural support vector machine~\citep{joachims2009cutting}. 
-The concept of structural support vector machines allows for a principled,
-maximum-margin based, loss-sensitive training of conditional random fields. Learning the potential yields much
+using a structural support vector machine (SSVM)~\citep{joachims2009cutting}. 
+The concept of SSVMs allows for a principled,
+maximum-margin based, loss-sensitive training of CRFs. Learning the potential yields much
 more complex interactions than the simple Potts potentials that are often used in the literature.
 
-In general, structural support vector machines learn the parameters $\theta$ of a predictor of the form
+In general, structural SSVMs learn the parameters $\theta$ of a predictor of the form
 \begin{equation}\eqlabel{prediction}
@@
 and AD$^3$ can work with arbitrary potential function, and allow precise
-learning using the structural support vector machine approach.
+learning using the SSVM approach.
 
@@
 hyper-parameter $C$ of the structural SVM formulation. These were adjusted
-using standard grid-search.
+using grid-search.
 We found 500 superpixels per image to work best, which allow for a maximum
@@
 however these results were not used for model selection. To separate
-the influence of loss-based training and the spatial reasoning of the conditional random field,
-we also train a standard support vector machine on the unary potentials for comparison.
+the influence of loss-based training and the spatial reasoning of the CRF,
+we also train a usual support vector machine (SVM) on the unary potentials for comparison.
 
@@
 This performance is still improved upon, both in class average and pixel
-average performance by the learned conditional random field approach, yielding
+average performance by the learned CRF approach, yielding
 the best published result so far for both measures. The increase over the
@@
 for the class imbalance, it has no way to make larger areas consistent, which
-the conditional random field can.
+the CRF can.
 On the other hand, performance of the CRF deteriorates slightly on very crowded
@@
 level. As the input from the random forest is also often of low quality for
-crowded scenes, the conditional random field has little chance to recover.
+crowded scenes, the CRF has little chance to recover.
 
@@
 \caption{%
-Qualitative evaluation of the conditional random field.
+Qualitative evaluation of the CRF.
 The first three images illustrate errors in the original prediction that can be corrected, while
@@
 \section{SUMMARY AND DISCUSSION}
-We introduce a conditional random field formulation for semantic segmentation
+We introduce a CRF formulation for semantic segmentation
 of structure classes in RGB-D images. We base our model in the output of an efficient GPU implementation
@@
 We combine color, depth and 3D orientation features into an energy function that is fully learned using 
- the structural support vector machine approach.  By explicitly modeling 3D
+ the SSVM approach. By explicitly modeling 3D
  relations in a fully learned framework, we improve the state-of-the art on the
@@
 local interactions. In future work, these interactions could be extended to
-larger areas using latent variable models~\citep{dann2012pottics} or higher
-order potentials~\citep{kohli2009robust}.
+larger areas using latent variable models or higher
+order potentials~\citep{ladicky2009associative}.
 Another possible line of future work is to combine our approach with a more
@@
 opening up the possibility to implement our approach entirely in real time.
-
 \printbibliography{}
-
 \end{document}

### 2013-09-14 paper.tex
squeezing and polishing
git-svn-id: https://svn.ais.uni-bonn.de/svn/staff/publications/icra_2014_mueller_nyu@4379 b2511e17-9ac0-488b-bc21-1d6d82e5baa2

@@
 in recent years.  Early work includes \citet{nuchter2008towards}, who combine
-6D SLAM, surface annotation and object recognition, to build semantically
+6D SLAM, surface annotation, and object recognition to build semantically
 annotated maps. They demonstrate their approach on a mobile robot in an indoor
@@
 stereo images. They approach the task by jointly reasoning about 3D layout and
-semantic of the scenes and produce a dense labeling on image level.  In
+semantics of the scenes and produce a dense labeling on image level.  In
 \citet{senguptaurban}, they extend their approach to produce a volumetric
@@
 volumetric representation. Their approach to image segmentation is build on
-the hierarchical CRF apporach of
+the hierarchical CRF approach of
 \citet{ladicky2009associative}, which is similar in spirit to our approach,
@@
 \citet{stuckler2012semantic} used a Random Forest model to obtain a dense
-semantic labeling of images, integrating predictions over multiple views in 3D.
-They evaluated their approach on a limited set of table-top and indoors scenes.
+semantic labeling of images and integrated predictions over multiple views in 3D.
+They evaluated their approach on table-top and simple indoors scenes.
 %
-\citep{silberman2011indoor} introduced the NYU Depth Dataset V1 indoor dataset,
-which consisted of a large variety of densely annotated indoor scences, captured as RGB-D images.
+\citet{silberman2011indoor} introduced the NYU Depth Dataset V1 indoor dataset,
+which consisted of a large variety of densely annotated indoor scenes, captured as RGB-D images.
 Their work also introduced a baseline method for semantic segmentation of RGB-D
-image, which used an approach based on superpixels, interest point descriptors
-and a CRF.
+image, which is based on a CRF over superpixels, with unary potentials given by interest point descriptors.
 While pairwise potentials for the CRF were carefully
@@
 %
-\citet{ren2012rgb} evaluated the design of features for semantic labeling of RGB-D data, and use
-a hierarchical segmentation to provide context. While they also define a CRF on superpixels,
-their model is again not learned, but a weighted Potts model, using only a
-probability of boundary map, and not taking spatial layout into account at all.
+\citet{ren2012rgb} evaluated the design of features for semantic labeling of
+RGB-D data, and use a hierarchical segmentation to provide context. While they
+also define a CRF on superpixels, their model is again not learned, but a
+weighted Potts model, using only a probability of boundary map, and not taking
+spatial layout into account at all.
 %
@@
 approach, we are not aware of any prior work on semantic annotation of 3D maps
-that fully learns their potentials. This allows our approach to infer
-the scene structure from the data, without the need to specify relevant relations
-by hand.
+that fully learns their potentials.
 %The task of dense semantic labeling in natural images has been widely studied
@@
     \end{center}
+    \vspace{-3mm}
     \caption{%
@@
     \figlabel{normal_feature}}
+    \vspace{-9mm}
 \end{figure}
@@
     vision literature, between the superpixel mean colors $c_i$ and $c_j$:
-    \[\exp\left(-\gamma \lVert c_i - c_j \rVert^2\right).\]
+    $\exp\left(-\gamma \lVert c_i - c_j \rVert^2\right)$.
 
@@
 measure accuracy for pixels without valid depth measurement.
+\vspace{-5mm}
 \end{table*}
@@
     \begin{center}
-        \includegraphics[width=.45\linewidth]{images/vertical_alignment}\vspace{1mm}
+        \includegraphics[width=.45\linewidth]{images/vertical_alignment}
     \includegraphics[width=.45\linewidth]{images/depth_difference}
     \end{center}
+    \vspace{-3mm}
     \caption{%
@@
     \figlabel{weights}}
+    \vspace{-3mm}
 \end{figure}
@@
 of random forest, and model spatial neighborhood using a superpixel-based approach.
-We combine color, depth and 3D orientation features into an energy function that is fully learned using 
- the SSVM approach. By explicitly modeling 3D
- relations in a fully learned framework, we improve the state-of-the art on the
- NYU V2 dataset for semantic annotation of structure classes.
+We combine color, depth and 3D orientation features into an energy function
+that is learned using the SSVM approach. By explicitly modeling 3D relations in
+a fully learned framework, we improve the state-of-the art on the NYU V2
+dataset for semantic annotation of structure classes.
 

### 2013-09-15 paper.tex
fix lineendings
git-svn-id: https://svn.ais.uni-bonn.de/svn/staff/publications/icra_2014_mueller_nyu@4380 b2511e17-9ac0-488b-bc21-1d6d82e5baa2
git-svn-id: https://svn.ais.uni-bonn.de/svn/staff/publications/icra_2014_mueller_nyu@4389 b2511e17-9ac0-488b-bc21-1d6d82e5baa2

@@
 reconstruction of the scene, together with a dense semantic labeling of the
-volumetric representation. Their approach to image segmentation is build on
+volumetric representation. Their approach to image segmentation builds on
 the hierarchical CRF approach of
@@
 RGB-D images, which are now easy to obtain using structured light sensors.
-\citet{stuckler2012semantic} used a Random Forest model to obtain a dense
+\citet{stuckler2012semantic}, for example, used a Random Forest model to obtain a dense
 semantic labeling of images and integrated predictions over multiple views in 3D.
@@
     \multicolumn{5}{@{}c@{}}{Ground Truth}\vspace{3mm}\\
-    \multicolumn{5}{@{}c@{}}{
+    \multicolumn{5}{@{}c@{}}{%
         \includegraphics[]{legend.pdf}
@@
 \caption{%
-Qualitative evaluation of the CRF.
+Qualitative evaluation of the CRF\@.
 The first three images illustrate errors in the original prediction that can be corrected, while

### 2014-01-25 paper.tex
camera ready
git-svn-id: https://svn.ais.uni-bonn.de/svn/staff/publications/icra_2014_mueller_nyu@4836 b2511e17-9ac0-488b-bc21-1d6d82e5baa2

@@
     \caption{%
-        Overview of the proposed semantic segmentation method.\label{teaser}
-    \figlabel{height}}
+        Overview of the proposed semantic segmentation method.\figlabel{teaser}
+    }
 \end{figure}
@@
 classes of props and furniture, which have smaller area than structure and
-floor.
+floor. The dataset is split into 795 images for training and 654 images for testing.
 
@@
 
-All hyper parameters were adjusted using 5-fold cross-validation. The
+All hyper parameters were adjusted using 5-fold cross-validation on the training set. The
 hyper parameters of the random forests were found using the \texttt{hyperopt}
@@
 possible performance of 95\% average class accuracy on the validation set.
+Training of the random forests took about 15 minutes on a NVIDIA GeForce GTX
+Titan. Training the structural SVM took 45 minutes on a Xeon X5650 CPU.
+Prediction using only the random forest takes 33ms on average, while segmentation and prediction
+using the structural SVM approximately take an additional 500ms.
 
@@
 crowded scenes, the CRF has little chance to recover.
+\Figref{weights} visualizes some learned potential functions.
 
@@
     \end{center}
-    \vspace{-3mm}
+    \vspace{-6mm}
     \caption{%
@@
     \figlabel{weights}}
-    \vspace{-3mm}
+    \vspace{-6mm}
 \end{figure}
 
-\Figref{weights} visualizes some learned potential functions.
 Higher values correspond to favored configurations. One can see that the
@@
 \section{SUMMARY AND DISCUSSION}
+\enlargethispage{5mm}
 We introduce a CRF formulation for semantic segmentation
-of structure classes in RGB-D images. We base our model in the output of an efficient GPU implementation
-of random forest, and model spatial neighborhood using a superpixel-based approach.
+of structure classes in RGB-D images. We base our model on the output of an
+efficient GPU implementation of random forest, and model spatial neighborhood
+using a superpixel-based approach.
 We combine color, depth and 3D orientation features into an energy function
 that is learned using the SSVM approach. By explicitly modeling 3D relations in
-a fully learned framework, we improve the state-of-the art on the NYU V2
+a fully learned framework, we improve the state-of-the-art on the NYU V2
 dataset for semantic annotation of structure classes.

### 2014-02-11 legend.tex
Minor.
git-svn-id: https://svn.ais.uni-bonn.de/svn/staff/publications/icra_2014_mueller_nyu@4878 b2511e17-9ac0-488b-bc21-1d6d82e5baa2

@@
     \begin{tikzpicture}
-        \matrix [column sep=.5cm]{%
-        \node [rectangle, fill=ground, minimum width=.5cm,minimum height=.5cm] {};&
-        \node [draw=none] {Ground};&
-        \node [rectangle, fill=structure, minimum width=.5cm,minimum height=.5cm] {};&
-        \node [draw=none] {Structure};&
-        \node [rectangle, fill=furniture, minimum width=.5cm,minimum height=.5cm] {};&
-        \node [draw=none] {Furniture};&
-        \node [rectangle, fill=prop, minimum width=.5cm,minimum height=.5cm] {};&
-        \node [draw=none] {Props};&
-        \node [rectangle, fill=black, minimum width=.5cm,minimum height=.5cm] {};&
-        \node [draw=none] {Void};\\
+        \matrix [column sep=.4cm]{%
+            \node [rectangle, fill=ground, minimum width=.4cm,minimum height=.4cm] {};&
+        \node [rectangle] {\sf \footnotesize\hspace*{-3ex} Ground};&
+        \node [rectangle, minimum width=.25cm] {};&
+        \node [rectangle, fill=structure, minimum width=.4cm,minimum height=.4cm] {};&
+        \node [rectangle] {\sf \footnotesize\hspace*{-3ex} Structure};&
+        \node [rectangle, minimum width=.25cm] {};&
+        \node [rectangle, fill=furniture, minimum width=.4cm,minimum height=.4cm] {};&
+        \node [draw=none] {\sf \footnotesize\hspace*{-3ex} Furniture};&
+        \node [rectangle, minimum width=.25cm] {};&
+        \node [rectangle, fill=prop, minimum width=.4cm,minimum height=.4cm] {};&
+        \node [draw=none] {\sf \footnotesize\hspace*{-3ex} Props};&
+        \node [rectangle, minimum width=.25cm] {};&
+        \node [rectangle, fill=black, minimum width=.4cm,minimum height=.4cm] {};&
+        \node [draw=none] {\sf \footnotesize\hspace*{-3ex} Void};\\
     };

### 2014-02-11 paper.tex
Minor.
git-svn-id: https://svn.ais.uni-bonn.de/svn/staff/publications/icra_2014_mueller_nyu@4878 b2511e17-9ac0-488b-bc21-1d6d82e5baa2

@@
 surroundings is essential. We formulate the problem of semantic annotation of maps
-as a dense labeling of RGB-D images into semantic classes. Dense labeling of objects
-and structure classes allows for a detailed reasoning about the scene.
+as a dense labeling of RGB-D images into semantic classes. Dense labeling of measured surfaces allows for a detailed reasoning about the scene.
 
 In this work, we propose the use of random forests combined with conditional
-random fields (CRFs) to perform robust estimation of structure classes in RGB-D
+random fields (CRF) to perform robust estimation of structure classes in RGB-D
 images. The CRF is learned using a structural support vector machine,
-allowing it to integrate the noisy low-level information produced by a pixel-based
+allowing it to integrate the noisy categorization produced by a pixel-based
 random forest to a consistent interpretation of the scene.
@@
 2D plane of the image, but also to model object distances and surface angles in
-3D, using a point cloud generated from the RGB-D image. The process is depicted
-in \Figref{teaser}.
+3D, using a point cloud generated from the RGB-D image. The process is illustrated
+in~\Figref{teaser}.
 
 We assess the accuracy of our model on the challenging NYU Segmentation V2
-dataset \citep{SilbermanECCV12}, where our model outperforms previous
+dataset~\citep{SilbermanECCV12}, where our model outperforms previous
 approaches.  Our analysis shows that while our random forest model
@@
 The task of dense semantic annotation of 3D maps has seen an increased interest
-in recent years.  Early work includes \citet{nuchter2008towards}, who combine
+in recent years.  Early work includes the approach of \citet{nuchter2008towards}, who combine
 6D SLAM, surface annotation, and object recognition to build semantically
-annotated maps. They demonstrate their approach on a mobile robot in an indoor
+annotated maps. The approach was demonstrated on a mobile robot in an indoor
 environment.
 %
-More recently \citet{sengupta2012automatic} introduced a dataset of
+More recently, \citet{sengupta2012automatic} introduced a dataset of
 semantically annotated street-scenes in a closed track, captured as pairs of
 stereo images. They approach the task by jointly reasoning about 3D layout and
-semantics of the scenes and produce a dense labeling on image level.  In
-\citet{senguptaurban}, they extend their approach to produce a volumetric
+semantics of the scenes and produce a dense labeling on image level.  
+\citet{senguptaurban} extended their approach to produce a volumetric
 reconstruction of the scene, together with a dense semantic labeling of the
-volumetric representation. Their approach to image segmentation builds on
+volumetric representation. This image segmentation method builds on
 the hierarchical CRF approach of
@@
 
-Recent approaches for indoor semantic annotation of maps mostly focused on
+Recent work on indoor semantic annotation of maps mostly focused on
 RGB-D images, which are now easy to obtain using structured light sensors.
-\citet{stuckler2012semantic}, for example, used a Random Forest model to obtain a dense
+\citet{stuckler2012semantic}, for example, used a Random Forest to obtain a dense
 semantic labeling of images and integrated predictions over multiple views in 3D.
@@
 %
-\citet{silberman2011indoor} introduced the NYU Depth Dataset V1 indoor dataset,
+\citet{silberman2011indoor} introduced the NYU Depth Dataset V1 dataset,
 which consisted of a large variety of densely annotated indoor scenes, captured as RGB-D images.
@@
 frequencies. This is in contrast to our work, which applies structured prediction techniques
-to learn potentials automatically to optimize predictive performance.
+to learn potentials that optimize predictive performance.
 %
 \citet{ren2012rgb} evaluated the design of features for semantic labeling of
-RGB-D data, and use a hierarchical segmentation to provide context. While they
-also define a CRF on superpixels, their model is again not learned, but a
+RGB-D data, and used a hierarchical segmentation to provide context. While they
+also defined a CRF on superpixels, their model is again not learned, but a
 weighted Potts model, using only a probability of boundary map, and not taking
@@
 %
-\citet{SilbermanECCV12} extended the NYU Depth Dataset V1 to the NYU Depth Dataset V2 that we are also
+\citet{SilbermanECCV12} extended the NYU Depth Dataset V1 to the NYU Depth Dataset V2 that we are 
 using in this work.  Their focus is on inferring support relations in indoor
@@
 
-\citet{stueckler2013} extends the approach of \citet{stuckler2012semantic} to
-a real-time system for online learning and prediction of semantic classes. Their
-use a GPU implementation of random forests, and integrate 3D scene information
+\citet{stueckler2013} extend the approach of \citet{stuckler2012semantic} to
+a real-time system for online learning and prediction of semantic classes. They use a GPU implementation of random forests, and integrate 3D scene information
 in an online fashion. They evaluate their approach on the dataset of
-\citet{SilbermanECCV12} with promising results.
+\citet{SilbermanECCV12} with good results.
 We use the implementation of random forest provided by
@@
 \citet{martins2011augmented}.  In contrast to graph-cut inference, fusion moves
-and AD$^3$ can work with arbitrary potential function, and allow precise
+and AD$^3$ can work with arbitrary potential functions, and allow precise
 learning using the SSVM approach.
@@
 The resulting superpixels are compact in the 2D image. As the density of the
-corresponding point cloud is dependent on the depth, we did not succeed in
+corresponding point cloud is dependent on depth, we did not succeed in
 creating superpixels that are compact in 3D while maintaining a meaningful
@@
 
-\emph{Constant}
+\noindent\emph{$\bullet$~Constant.}
     A constant feature allows to model general neighborhood relations.
 
-\emph{Color Contrast}
+\noindent\emph{$\bullet$~Color Contrast.}
     We employ a non-linear color contrast, as is common in the computer
@@
 
-\emph{Vertical Alignment}
+\noindent\emph{$\bullet$~Vertical Alignment.}
     We model the directed angle between superpixel centers in the 2D image
@@
 
-\emph{Depth Difference}
+\noindent\emph{$\bullet$~Depth Difference.}
     We include the signed depth difference between superpixels, which
@@
 
-\emph{Normal Orientations}
+\noindent\emph{$\bullet$~Normal Orientations.}
     Differences in normal vector orientation are a strong clue on
@@
     to two adjacent superpixels.  
-    The feature is illustrated in \Figref{normal_feature}. The change
+    An example is shown in \Figref{normal_feature}. The change
     in normal orientation highlights that pillow and wall are distinct
@@
 We evaluate our approach on the public NYU depth V2 segmentation dataset of
-indoor scenes.  The dataset comes with a detailed annotation of 1449 indoor
+indoor scenes.  The dataset comes with a detailed annotation of 1449 
 RGB-D images belonging to a wide variety of indoor scenes, categorized into 26
@@
 We optimize our model for \emph{average class accuracy} (the mean of the
-diagonal of the confusion matrix), which puts more emphasis on the harder
+diagonal of the confusion matrix), putting more emphasis on the harder
 classes of props and furniture, which have smaller area than structure and
@@
 Our approach is implemented using our \textsc{PyStruct}
-library\footnote{\url{http://pystruct.github.io}}.  The code for our
-experiments will be released upon acceptance. We use \textsc{scikit-learn}~\citep{pedregosa2011scikit}
+library\footnote{\url{http://pystruct.github.io}}.  We use \textsc{scikit-learn}~\citep{pedregosa2011scikit}
 for $k$-means clustering and the SVM baseline.
 
-All hyper parameters were adjusted using 5-fold cross-validation on the training set. The
+All hyper-parameters were adjusted using 5-fold cross-validation on the training set. The
 hyper parameters of the random forests were found using the \texttt{hyperopt}
-framework of \cite{bergstra2011algorithms}. For the CRF model, the only
+framework~\cite{bergstra2011algorithms}. For the CRF model, the only
 hyper-parameters are related to the superpixel segmentation, and the single
 hyper-parameter $C$ of the structural SVM formulation. These were adjusted
-using grid-search. 
+using grid search. 
 We found 500 superpixels per image to work best, which allow for a maximum
 possible performance of 95\% average class accuracy on the validation set.
-Training of the random forests took about 15 minutes on a NVIDIA GeForce GTX
-Titan. Training the structural SVM took 45 minutes on a Xeon X5650 CPU.
-Prediction using only the random forest takes 33ms on average, while segmentation and prediction
-using the structural SVM approximately take an additional 500ms.
+Training of the random forests took about 15\,minutes on a NVIDIA GeForce GTX
+Titan. Training the structural SVM took 45\,minutes on a Xeon X5650 CPU.
+Prediction using only the random forest takes 33\,ms on average, while segmentation and prediction
+using the structural SVM approximately take an additional 500\,ms.
 
@@
 validation data. We now report accuracies of simpler models for reference,
-however these results were not used for model selection. To separate
+but these results were not used for model selection. To separate
 the influence of loss-based training and the spatial reasoning of the CRF,
@@
 using a standard unstructured SVM with rescaled loss already advances the mean
-accuracy decidedly above the previous state-of-the art. We
+accuracy above the previous state-of-the art. We
 attribute this mostly to the ability of the SVM to exploit correlation between
@@
 crowded scenes, the CRF has little chance to recover.
-\Figref{weights} visualizes some learned potential functions.
 
@@
     \caption{%
-        Visualization of some of the learned potentials. The right potential is
-        applied to relative depth between superpixels, the second on the
-        feature encoding whether one superpixel is above the other in the
-        image. See \secref{results} for details.
+        Visualization of some of the learned potentials. The left potential is
+        on the feature encoding whether one superpixel is above the other in the
+        image. The right potential is applied to the relative depth between superpixels. See \secref{results} for details.
     \figlabel{weights}}
@@
 
+\Figref{weights} visualizes two of the learned potential functions.
 Higher values correspond to favored configurations. One can see that the
@@
 \begin{figure*}
+    {\setlength{\tabcolsep}{1mm}\sf \footnotesize 
     \begin{tabu} to \linewidth{@{}XXXXX@{}}
@@
     \end{tabu}
-\caption{%
+}\caption{%
 Qualitative evaluation of the CRF\@.
@@
 local interactions. In future work, these interactions could be extended to
-larger areas using latent variable models or higher
-order potentials~\citep{ladicky2009associative}.
+larger areas using latent variable models or higher order potentials~\citep{ladicky2009associative}.
 Another possible line of future work is to combine our approach with a more
@@
 processing~\citep{stueckler2013}. The SLIC superpixel algorithm can also be
-implemented on GPU in real-time, as was demonstrated by \citep{ren2011gslic}, and similarly
+implemented on GPU in real-time, as was demonstrated by \citet{ren2011gslic}, and similarly
 the normal features we use also have
@@
 opening up the possibility to implement our approach entirely in real time.
+
 \printbibliography{}

### 2014-02-15 paper.tex
build paper, fixed cite to citep
git-svn-id: https://svn.ais.uni-bonn.de/svn/staff/publications/icra_2014_mueller_nyu@4892 b2511e17-9ac0-488b-bc21-1d6d82e5baa2
Trying to give a better explanation of the learened potentials.
git-svn-id: https://svn.ais.uni-bonn.de/svn/staff/publications/icra_2014_mueller_nyu@4893 b2511e17-9ac0-488b-bc21-1d6d82e5baa2

@@
 floor. The dataset is split into 795 images for training and 654 images for testing.
-
+%
 Our approach is implemented using our \textsc{PyStruct}
@@
 hyper parameters of the random forests were found using the \texttt{hyperopt}
-framework~\cite{bergstra2011algorithms}. For the CRF model, the only
+framework~\citep{bergstra2011algorithms}. For the CRF model, the only
 hyper-parameters are related to the superpixel segmentation, and the single
@@
 
+\vspace{-2mm}
 \subsection{Results}\seclabel{results}
+\vspace{-1mm}
 \Tabref{results} compares different components of our approach with the literature.
@@
 results that are very close to the ground truth in several complex scenes.
-
+%
 We found that our approach improves results most for scenes with a clear geometric structure,
@@
 \Figref{weights} visualizes two of the learned potential functions.
-Higher values correspond to favored configurations. One can see that the
-vertical alignment potential expresses that the floor is much more likely to be below
-other classes. It also encodes the fact that props
-rest on furniture, but not the other way around.
-The potential of the depth feature encodes, for example, that the ground
-is usually behind the other classes, while furniture is in front of structures,
-such as the wall.
-Interestingly, the potential functions are not anti-symmetric, and forcing them to be so
-degrades the results. This suggests that the direction of connecting edges, going from
-the top left to the bottom right in the image, is also exploited by the potentials.
+Higher values correspond to favored configurations. We did not force potentials
+to be symmetric or anti-symmetric, which makes interpretation of the figures a
+bit harder, but increases performance.
+Edges are constructed to go from top left to bottom right. Potentials below the
+diagonal are those for an edge going from a label given by the column to the
+one given by the row, while the ones above the diagonal are for the opposite
+direction.  For vertical alignment, one would therfore expect to find
+anti-symmetric potentials. However the left-right direction
+seems to also contain useful information, breaking the symmetry.
+One can see that the vertical alignment potential expresses that the floor is
+much more likely to be below other classes. It also encodes the fact that props
+rest on furniture, but not the other way around.  The potential of the depth
+feature encodes, for example, that the ground is usually behind the other
+classes, while furniture is in front of structures, such as the wall.
 
@@
 \end{figure*}
-
 \section{SUMMARY AND DISCUSSION}
@@
 dataset for semantic annotation of structure classes.
-
+%
 While our approach allows modeling of spatial relations, these are limited to
@@
 individual views in 3D to exploit temporal coherence.
-
+%
 While this work did not explicitly address real time application, the random
